### 2020-05-03 docs/build/assets/AlgebraicLoop/algebraicloop.tex
Revised docs.

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \matrix (m) [
            matrix of nodes, 
            ampersand replacement=\&, 
            column sep = 1cm, 
            row sep = 1cm, 
            nodes={
                text height=1.5ex,
                text depth=.25ex,
                anchor=center}
                ]{
                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writer) {Component={writer}}; \\
                };

        % Draw connections 
        \begin{scope}[line width=1.5mm, >={Triangle[width=4mm,length=3mm]}]
            \def\shiftamount{0.5mm};
            \draw[->] (gen-edge.east) -- (adder-edge.west);
            \draw[->] (adder-edge.east) -- (gain-edge.west);
            \draw[->] (gain-edge.east) -- (writer-edge.west);
            \draw[->] (gain-edge.east) -- (writer-edge.west);
            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
            \draw[->] ([yshift=0.75mm] a) -| (adder-edge.south);
        \end{scope}

        % \Place clock 
        \begin{scope}[shift={(-4cm, -2cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] (-4.5, -3) rectangle (4.5, 1);
        \draw (0,0) node[yshift=-2.5cm, xshift=3.5cm]{Model};
    \end{tikzpicture}
\end{document}

>>>>

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \matrix (m) [
            matrix of nodes, 
            ampersand replacement=\&, 
            column sep = 1cm, 
            row sep = 0.5cm, 
            nodes={
                text height=1.5ex,
                text depth=.25ex,
                anchor=center}
                ]{
                     \& \draw pic (writerin) {Component={writerin}}; \& \&  \\
                    \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \& \draw pic (writerout) {Component={writerout}}; \\
                };

        % Draw connections 
        \begin{scope}[line width=1.5mm, >={Triangle[width=4mm,length=3mm]}]
            \def\shiftamount{0.5mm};
            \draw[->] (gen-edge.east) -- node[midway, anchor=north]{$r(t)$} (adder-edge.west);
            \draw[->] (adder-edge.east) -- node[midway, anchor=north]{$u(t)$} (gain-edge.west);
            \draw[->] (gain-edge.east) -- (writerout-edge.west);
            \draw[->] (gain-edge.east) -- (writerout-edge.west);
            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
            \draw[->] ([yshift=0.75mm] a) -| node[midway, xshift=1.75cm, anchor=north]{$y(t)$} (adder-edge.south);
            \draw[-] (gen-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
            \draw[->] (b) |- (writerin-edge.west);
        \end{scope}

        % \Place clock 
        \begin{scope}[shift={(-4.5cm, -2.25cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] (-5, -3) rectangle (5, 1.5);
        \draw (0,0) node[yshift=-2.5cm, xshift=4cm]{Model};
    \end{tikzpicture}
\end{document}
